---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# billboardAnalysis

<!-- badges: start -->
<!-- badges: end -->

The goal of this R package is to create an interactive Shiny dashboard that lets users explore Billboard and Spotify data from the 2010s, focusing on trends in audio features like energy, acousticness, and danceability.

## Installation

You can install the development version of billboardAnalysis with:

``` r
# install.packages("devtools")
devtools::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-bigchayanont")
```

## Example

```{r example}
library(billboardAnalysis)
## basic example code
```

To access to the dataset. 

**Billboard Dataset:**

```{r}
head(audio_features)
```

**Song features from Spotify Dataset:**

```{r}
head(billboard)
```

**A combination of billboard and spotify dataset in long format:** 

```{r}
head(feature_long)
```


To access to the shiny dashboard

```{r eval=FALSE}
run_app()
```

