---
title: "Song Billboard Analysis in the 2010s"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Song Billboard Analysis in the 2010s}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(billboardAnalysis)
```

# Introduction

This package presents an analysis of songs that charted on Billboard throughout the 2010s. The goal is to understand trends in audio features of popular songs and their relationship with chart performance using shiny dashboard.

# Data Overview

The analysis utilizes two primary datasets:

-   Billboard Dataset: Contains information about songs that appeared on the Billboard charts, including song titles, performers, chart positions, and weeks on the chart.
-   Spotify Dataset: Includes detailed audio features of songs, such as energy, acousticness, danceability, and speechiness, along with popularity scores.

# Key Findings

  -   Trends in Audio Features: Significant trends in audio features, such as variations in energy and danceability, are observed across different years.
  -   Correlation with Popularity: Features like energy and danceability show strong correlations with song popularity, indicating that upbeat and energetic tracks tend to perform better.
  -   Long-Lasting Tracks: Songs that remained on the charts for extended periods exhibit distinct patterns, shedding light on what contributes to their longevity.

Example: 

Spotify Dataset: 
```{r}
head(audio_features)
```

Billboard Dataset:
```{r}
head(billboard)
```


# R shiny dashboard

This Shiny app, Song Billboard Analysis in the 2010s, allows users to interactively explore Billboard chart data from 2010 to 2019, enriched with Spotify audio features. The dashboard offers visualizations of audio trends over time, distribution of audio features, and a comparison of these features across genres. Key widgets include a year range selector, performer filter, and feature comparison tools. A help mode switch provides descriptions and insights for each plot and input field, making it user-friendly for those unfamiliar with audio feature analysis.

To access to the shiny dashboard

```{r eval=FALSE}
run_app()
```

For more details, visit the package documentation or the [GitHub](https://github.com/ETC5523-2024/assignment-4-packages-and-shiny-apps-bigchayanont) page.


	

